---
title: "igraph intro"
output: html_notebook
---

See this amazing tutorial for details of igraph: http://kateto.net/networks-r-igraph
```{r}
library(igraph)
# graph is defined by edges, given as in, out, in, out ... list
g2 <- graph( edges=c(1,2, 2,3, 3, 1), n=2 )
plot(g2)
# ?igraph.plotting
```

```{r}
path <- "./asp/Networks/n1.edges"
mydata <- read.table(path, sep=" ", skip=2)
vlist <- Reduce(c, t(mydata))  # this must be improved for large datasets...
g <- graph(vlist+1) # igraph doesn't like 0s as ids
plot(g)

# even a simpler way of doing the same thing with library function. Further columns of the df are treated as edge attributes. May provide vertices=df as well
net <- graph_from_data_frame(d=mydata, directed=T)
plot(net)
```
We can play a bit with various representations of a graph:
```{r}
g
E(g)
V(g)
g[]
```
And easily add some properties of edges and nodes alike:
```{r}
V(g)$name <- 15:29
plot(g)
g$name <- "n1"
graph_attr(g)
```
Note there are some keyword attributes: name, weight and type which alter execution of some methods by indicating the graph is named, weighted or bipartite respectively.

Some useful graph constructors:
```{r}
plot(make_full_graph(10))
s <- make_star(10)
plot(s, layout=layout_in_circle)
plot(rewire(s, each_edge(prob=0.7)), layout=layout_in_circle) # simple method for changing the graph a bit

tr <- make_tree(20, children = 3, mode = "in")
plot(tr, vertex.label=NA)

plot(s %du% tr, vertex.size=10, vertex.label=NA) # disjoint union
```
Some nice export features:
```{r}
as_edgelist(net, names=T)

as_adjacency_matrix(net)

as_data_frame(net, what="edges")
```
But let's perform some maths instead:
```{r}
diameter(net) # the longest distance in this graph
get_diameter(net) # also return one of the paths
mean_distance(net, directed=F)
distances(net)
```
```{r}
deg <- degree(net, mode="all")

plot(net, vertex.size=deg*5)
```

