---
title: "Calling C functions"
output: html_notebook
---

Requirements on the C function are:

1.  Must not return anything (void)
2.  Must take only pointers as arguments. Scalars are vectors length 1

To include a new function into a shared library:

1. Create a .c file
2. In the terminal run `R CMD SHLIB doubler.c`
3. In your R file call:
    dyn.load("doubler.so")  # load the function under it's original name
    .C("double_me", x = as.integer(5))  # call, all parameters must be pointers
```{r}
# dyn.load("doubler.so")
# .C("double_me", x = as.integer(5))
```

There are 2 other ways to accomplish the same task. You can either use .Call which is bloody complicated and recommended way for professionals or use Rcpp which should cover both C and C++. Let's have a look:

Create file with normal C function, add some headers and a magic comment. See doubler3.cpp for details.
Then just execute:
```{r}
# library(Rcpp)
# sourceCpp("doubler3.cpp")
# double_me3(5)
```
Voila! Works like a charm.
Limitations: file may not have dependencies other than R packages (see Rcpp::depends). Long -> numeric conversion is dangerous etc.
Source: http://anythingbutrbitrary.blogspot.co.uk/2014/02/three-ways-to-call-cc-from-r.html


Tests:
1. Run POETS function with any efficiency overhead %>% commit
2. Pass data from igraph object %>% commit
3. design %>% Precompute adjacency list (with R or C) %>% commit

```{r}
library(Rcpp)
sourceCpp("their_bfs.cpp")
path <- paste0("/home/hubert/Code/Warwick/BSP/", "external/asp/Networks/n5.edges")
Cbfs(path)
```

