---
title: "Analysis of the POETS graphs"
output: html_notebook
---

### Analysing existing dataset
First, let's import one of the POETS graphs:
```{r}
library(igraph)
library(magrittr) # pipe operator
library(devtools)
document(pkg = "./src/bspLib/")
library(bspLib) # my library
getwd()

data <- read.table("./external/asp/Networks/n5.edges", sep=" ", skip=2)
n5 <- graph_from_data_frame(d = data, directed=T)
rm(data) # remove name from workspace to reduce clutter
```

And calculate some descriptive statistics:
```{r}
gorder(n5)  # number of vertices
gsize(n5)  # number of edges
```
In degree plotted in red, out degree in green:
```{r}
{  plot(table(degree(n5, mode = "in")), type = "p", col="red", ylab = "occurences", xlab = "degree")
   points(table(degree(n5, mode = "out")), type = "p", col=3)}
```
Is there any correlation between in and out degree?
```{r}
cor.test(degree(n5, mode = "in"), degree(n5, mode = "out"))$estimate
```
Examining these plots I conjectured distribution of degrees is log-normal shifted by a constant factor (0 cannot be obtained otherwise). Fitting a suitable `lnorm3` gives:
```{r}
lnorm_fit <- bspLib::lnorm3_autofit(degree(n5, mode = "all"))
plot(lnorm_fit)
```
The fit looks really accurate. It's now possible to generate a new random graph using this estimate as degree distribution: 
```{r}
g5 <- graphFromDist(gorder(n5) %>% round, lnorm_fit)
qqplot(degree(g5, mode="all"), degree(n5, mode="all"))
```
Nearly perfect, just the tail is a bit fussy.
