---
title: "Analysis of the POETS graphs"
output: html_notebook
---

### Analysing existing dataset
```{r message=FALSE, warning=FALSE, include=FALSE}
library(bspLib) # my library
```
First, let's import one of the POETS graphs:
```{r}
data <- read.table(here("external", "asp", "Networks", "n5.edges"), sep=" ", skip=2)
n5 <- graph_from_data_frame(d = data, directed=T)
rm(data) # remove name from workspace to reduce clutter
```

And calculate some descriptive statistics:
```{r}
gorder(n5)  # number of vertices
gsize(n5)  # number of edges
```
In degree plotted in red, out degree in green:
```{r echo=FALSE}
{  plot(table(degree(n5, mode = "in")), type = "p", col="red", ylab = "occurences", xlab = "degree")
   points(table(degree(n5, mode = "out")), type = "p", col=3)}
```
Is there any correlation between in and out degree?
```{r}
cor.test(degree(n5, mode = "in"), degree(n5, mode = "out"))$estimate
```
Examining these plots I conjectured distribution of degrees is log-normal shifted by a constant factor (0 cannot be obtained otherwise). Fitting a suitable `lnorm3` gives:
```{r}
lnorm_fit <- bspLib::lnorm3_autofit(degree(n5, mode = "all"))
plot(lnorm_fit)
```
The fit looks really accurate. It's now possible to generate a new random graph using this estimate as degree distribution: 
```{r}
g5 <- graphFromDist(gorder(n5) %>% round, lnorm_fit)
qqplot(degree(g5, mode="all"), degree(n5, mode="all"))
```
Nearly perfect, just the tail is a bit fussy.


### Statistics for all the graphs
```{r}

netNames <- list.files(here("external", "asp", "Networks"))
nets <- netNames %>% lapply(function(x) {
                              bspLib::readPOETSGraph(here("external", "asp", "Networks", x))
                         })
preds <- nets %>% sapply(function(x) bspLib::lnorm3_autofit(degree(x)))
preds["estimate",]
df <- data.frame(preds["estimate",] %>% sapply(c) %>% t,
                 nodes = sapply(nets, gorder),
                 edges = sapply(nets, gsize),
                 names = netNames)
```
Artificial graphs:
```{r}
range <- 5:8
df$m
plot(df[range, c("nodes", "meanlog", "threshold")])
```
Natural graphs:
```{r}
fitdist(degree(nets[[1]]), distr="norm") %>% plot
fitdist(degree(nets[[2]]), distr="exp") %>% plot
fitdist(degree(nets[[3]]), distr="exp") %>% plot
fitdist(degree(nets[[4]]), distr="exp") %>% plot
```
```{r}
preds[,1]
```

